Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-10-06 bbbq_article.tex
Explain how we chose the MHC-I allotypes, fix #234

For MHC-I, 9-mers were used, 
as this is the length most frequently presented in MHC-I 
and was used in our earlier study \cite{bianchi2017}. 
For MHC-II, 14-mers were used, 
as these are the most frequently occurring epitope length \cite{bergseng2015different}.
A human (UniProt ID UP000005640\_9606), 
viral (SARS-CoV-2, UniProt ID UP000464024) 
and bacterial (\emph{Mycobacterium tuberculosis}, UniProt ID UP000001584) 
reference proteome was used. 
\verb;TMHMM; \cite{krogh2001predicting} was used to predict the topology 
of the proteins within these proteomes.
To predict the affinity of an epitope to a certain MHC haplotype,
 \verb;EpitopePrediction; \cite{bianchi2017} for MHC-I 
and \verb;MHCnuggets; \cite{shao2020high} for MHC-II was used.
For MHC-II, haplotypes were selected with a phenotypic frequency 
of at least 14\% in the human population \cite{greenbaum2011functional},
resulting in 21 MHC-II haplotypes.

>>>>

For MHC-I, 9-mers were used, 
as this is the length most frequently presented in MHC-I 
and was used in our earlier study \cite{bianchi2017}. 
For MHC-II, 14-mers were used, 
as these are the most frequently occurring epitope length \cite{bergseng2015different}.
A human (UniProt ID UP000005640\_9606), 
viral (SARS-CoV-2, UniProt ID UP000464024) 
and bacterial (\emph{Mycobacterium tuberculosis}, UniProt ID UP000001584) 
reference proteome was used. 
\verb;TMHMM; \cite{krogh2001predicting} was used to predict the topology 
of the proteins within these proteomes.
To predict the affinity of an epitope to a certain MHC haplotype,
 \verb;EpitopePrediction; \cite{bianchi2017} for MHC-I 
and \verb;MHCnuggets; \cite{shao2020high} for MHC-II was used.
Both MCH-I and MHC-II haplotypes were selected to have a high occurrance,
where the MHC-I haplotypes are the same 13 haplothose used in our earlier study \cite{bianchi2017},
and the 21 MHC-II, haplotypes have a phenotypic frequency 
of 14\% or more in the human population \cite{greenbaum2011functional}.
